---
title: "Assignment0"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
##Name: Mohamed Ali Slim
##Username: IsolatedPhoenix
##Document: [link](https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf)

##Abstract
In this assignment, we are displaying basic applications and my ability to complete them correctly using R programming. There are 14 ToDo's plus a final extra Todo requested to be done that are found in the document linked above and the results with their code can be found below.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###3.1 - Calculator

```{r calc}
((2018-2015)/(2018-1997))*100
```

###3.2 - Workspace

```{r work}
ysu=2018-2015
ysa=2018-1997
a=ysu/ysa
a=a*100
a
```

###3.4 - Functions

```{r func}
a=c(4,5,6,11)
sum(a)
```

###3.5 - Plots

```{r plot}
x=rnorm(100)
plot(x)
```

###4 - Help & Documentation

```{r help}
help(sqrt)
```

###5 - Scripts

```{r script}

file.create("firstscript.R")
x=rnorm(100)
plot(x)
source("firstscript.R")
```

###6.2 - Matrices

```{r mat}
p = 31:60
Q = matrix(data=p, nrow = 6, ncol = 5)
Q
```

###6.3 - Data Frames

```{r data}
x1=rnorm(100)
x2=rnorm(100)
x3=rnorm(100)
t=data.frame(a=x1, b=x1+x2, c=x1+x2+x3)
plot(t)
```

###7 - Graphics

```{r graphics}
x1=rnorm(100)
x2=rnorm(100)
x3=rnorm(100)
t=data.frame(a=x1, b=x1+x2, c=x1+x2+x3)
plot(t$a, type="l", ylim=range(t), lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s",lwd=2, col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4, col=rgb(0,0,1,0.3))
?rgb
```

###8 - R&W data Files

```{r file}
a=read.table("tst1.txt", header=TRUE)
write.table(a$g*5, file = "tst2.txt", row.names = FALSE)
```

###9 - not available data

```{r nope}
mean(sqrt(rnorm(100)))
```

###10.2 - dates

```{r dates}
x = c(strptime(c("20180202", "20181221","20180808"),format="%Y%m%d"))
y = c(1,6,3)
plot(x,y, xlab = "Date",ylab="presents",main = "How gifted I am")
```

###11.2 - For Loop

```{r for}
a=seq(from=1, to=100)
s=c()

for(i in 1:100)
  {
  if(a[i]<5 | a[i]>90)
    {
      s[i]=a[i]*10
  }else{
      s[i]=a[i]*.1
    }
  }
s
```

###11.3 - Writing your own function

```{r arg}
p=1:100
fun1 <- function(arg) 
{
s=c()
for(i in 1:length(arg))
  {
  if(arg[i]<5 | a[i]>90)
    {
      s[i]=arg[i]*10
  }else{
      s[i]=arg[i]*.1
    }
  }  
return(s)  
}
fun1(p)
```

###FINAL TODO

```{r note}
p=1:100

fun2 <- function(a)
{
b=(a[a <5 | a >90])*10
c=(a[a<=90 & a>=5])*.1
s=c(b,c)
return(s)  
}
fun2(p)
```
